### 2019-09-27 paper/conclusion.tex
Revised based on reviewer's comments

In the present paper, five different types of initial fissile materials have been studied for transitioning to thorium fuel cycle in the \gls{SD-TMSR}. The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}. We adopted two different feed mechanisms; thorium feed mechanism and non-thorium feed mechanism. The whole-core of the SD-TMSR was simulated with Pu reactor-grade, TRU, and $^{233}$U as initial fissile materials. Besides, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated. Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel. Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. in addition, the Pu proportion in fuel salt has been calculated and found to be below the solubility limit. Finally, the neutron flux spectrum for the three selected cases has been described.

>>>>

In the present paper, five different types of initial fissile materials have been studied for transitioning to thorium fuel cycle in the \gls{SD-TMSR}. The molar composition of start-up fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}. We adopted two different feed mechanisms; thorium feed mechanism and non-thorium feed mechanism. The whole-core of the SD-TMSR was simulated with Pu reactor-grade, TRU, and $^{233}$U as initial fissile materials. Additionally, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated. Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U start-up fuel. Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. in addition, the Pu proportion in fuel salt has been calculated and found to be below the solubility limit. Finally, the neutron spectrum shift during the reactor operation for the three selected cases has been calculated.

### 2019-09-27 paper/introduction.tex
Revised based on reviewer's comments

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation nuclear systems. These goals are; safety and reliability, economics, sustainability, and non-proliferation and physical protection \cite{doe2002technology}. \glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}. Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl). This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.

@@

Betzler, et al. discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}. They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}. Zou, et al. introduced two ways for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition. In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality. In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Meanwhile, Zou, et al. studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel. They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU) \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U. Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature. Therefore, the present paper discusses the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition. To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF \cite{de2000scenarios}. Moreover, two different feed mechanisms are used: \\
(1)Th + $^{233}$U from Pa-decay tank (i.e. removal mass rate (Pa-233) = feed mass rate ($^{233}$U)) \cite{betzler2016modeling}.\\
(2)continuous feed flow of (HM except for Th) + some or all $^{233}$U from Pa-decay tank.\\
This present paper is organized as follows: after an introduction on \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.

>>>>

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation nuclear systems. These goals are; safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}. \glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}. Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl). This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.

@@

Betzler, et al. discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}. They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}. Zou, et al. introduced two approaches for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition. In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality. In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Meanwhile, Zou, et al. studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel. They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU) \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U. Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature. Therefore, the main object of the present paper is to discuss the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition. To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF \cite{de2000scenarios}. Moreover, two different feed mechanisms are used as follows:
\begin{itemize}
	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}
This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.

### 2019-09-27 paper/methods.tex
Revised based on reviewer's comments

\section{Model description}
\subsection{Geometry}
The \gls{SD-TMSR} design model was introduced by the \gls{CAS} during the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)" in 2011 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The design of \gls{SD-TMSR} is inspired by \gls{MSBR} \cite{robertson_conceptual_1971} after some modification in the geometry to control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} model is described deeply in \cite{li_optimization_2018}.
Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the \gls{SD-TMSR}. The active zone is a right cylinder with height and diameter equal to 460 cm. Assemblies of graphite\footnote{Density of graphite 2.3 g/cm$^3$.} hexagonal prisms fill the core. The side length of the graphite hexagonal prism was optimized in \cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates continuously through the fuel channels that pierces the graphite hexagonal prisms. The active zone is divided into two different zones to enhance Th-U breeding performance. The radius of the fuel tubes in the outer zone is 5 cm and the radius of the fuel tubes in the inner zone is 3.5 cm. Moreover, axial and radial reflectors from graphite surround the active zone to maximize neutron flux. The core is surrounded by B${_4}$C cylinder that acts as a shield against heat and neutrons radiation. 
Another Ni-based (hastelloy N) cylinder surrounds the whole core and provides structure and heat protection. The main characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.jpg}
	\caption{The quarter-core model configuration of the SD-TMSR a) Longitudinal view b) cross-sectional view at the horizontal midplane.}
	\label{fig:ff}
\end{figure}

@@

Simulation of Liquid-fueled Molten Salt Reactor (MSR) systems requires computational software that must support online fuel salt reprocessing and refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 beta\footnote{SERPENT-2 is a \gls{3D} continuous energy Monte Carlo neutron transport and burn-up code.} \cite{leppanen2014serpent} is used to simulate the full-core of the SD-TMSR with different types of initial fuel. The extension of SERPENT code accounts for continuous online reprocessing and refueling \cite{aufiero2013extended}. Meanwhile, ENDF-VII.0 cross-section library is adopted for all calculations. The results demonstrate full-core runs of 12.5E+06 neutron history per depletion step. The full burnup time of the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ $36$ $pcm$. The online extraction of \gls{FPs} and noble gases  provides many benefits for MSRs. For example, it would reduce the fissile inventory required to achieve criticality and improve the breeding ratio.
Figure~\ref{fig:flow} shows a flow chart of the calculation steps.

@@

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time\footnote{The extraction time depends on the type of material and its impact on the neutron economy, for instance, the extraction time of the gaseous \gls{FPs} is 30 seconds and for lanthanides and other soluble metals is $\approx$10.59 days in this work.}. This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the gas-tank\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}. Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, pa-tank\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U. SERPENT-2 subroutine allows changes the flow rates of the isotopes during reactor operation \cite{aufiero2013extended}. The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle (i.e. 1 year). Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.

\section{Feed and extraction rates}
In the present work, two different feed mechanisms are used. The first mechanism allows continuous feed flow of thorium and $^{233}$U from Pa-decay tank. In contrast, the second mechanism adopts continuous feed flow of $^{233}$U from Pa-decay tank and the same composition of the initial fuel except for thorium. \\
The fission products act as poisons in the MSRs; they negatively impacting the reactivity. Therefore, \gls{FPs} must be extracted during reactor operation. Consider $T_{r}$ as the time during which the total fuel salt is reprocessed and $dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}

@@

\begin{table}[ht!]
	\centering
	\caption{The reprocessing table.} 
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|s|p{2cm}|}
		\hline
		\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reproc- essing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
		\hline
		Gaseous \gls{FPs} and non-dissolved metals  &  Atomic number (Z) = 1, 2, 7, 8,10, 18, 36, 41, 42, 43, 44, 45, 46, 47, 51, 52, 54, 71, 72, 73, 74, 75, 76,77, 78, 79 and 86.			&	30s	&  -3.333E-02 \\
		\hline
		Lanthanides and other soluble \gls{FPs}     & Atomic number (Z) = 30, 31,32, 33, 34, 35, 37, 38, 39, 40, 48, 49, 50, 53, 55, 56, 57, 58, 59, 60, 61,62, 63, 64, 65, 66, 67, 68, 69 and 70. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
		\hline
		Protactinium   & Pa  &  10.599 d (5 m$^3$/d)  &  -1.092E-06 \\
		\hline
	\end{tabularx}
	\label{tab:table6}
\end{table}

>>>>

\section{Model description}
\subsection{Geometry}
The \gls{SD-TMSR} design model was introduced by the \gls{CAS} during the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)" in 2011 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The design of \gls{SD-TMSR} is inspired by \gls{MSBR} \cite{robertson_conceptual_1971} after some modification in the geometry to control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} model is described deeply in \cite{li_optimization_2018}.
Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the \gls{SD-TMSR}. The active zone is a right cylinder with height and diameter equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of $2.3$ g/cm$^3$, to validate our results against results in the literature \cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the core. The side length of the graphite hexagonal prism was optimized in \cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates continuously through the fuel channels that pierces the graphite hexagonal prisms. The active zone is divided into two different zones to enhance Th-U breeding performance. The radius of the fuel tubes in the outer zone is 5 cm and the radius of the fuel tubes in the inner zone is 3.5 cm. Moreover, axial and radial reflectors from graphite surround the active zone to maximize neutron flux. The core is surrounded by B${_4}$C cylinder that acts as a shield against heat and neutrons radiation. 
Another Ni-based (hastelloy N) cylinder surrounds the whole core and provides structure and heat protection. The main characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{The quarter-core model configuration of the SD-TMSR a) Longitudinal view b) Cross-sectional view at the horizontal midplane.}
	\label{fig:ff}
\end{figure}

@@

Simulation of Liquid-fueled Molten Salt Reactor (MSR) systems requires computational software that must support online fuel salt reprocessing and refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 beta\footnote{SERPENT-2 is a \gls{3D} continuous energy Monte Carlo neutron transport and burn-up code.} \cite{leppanen2014serpent} is used to simulate the full-core of the SD-TMSR with different types of initial fuel. The extension of SERPENT code accounts for continuous online reprocessing and refueling \cite{aufiero2013extended}. Meanwhile, ENDF-VII.0 cross-section library is adopted for all calculations. The results demonstrate full-core runs of $12.5E+06$ neutron history per depletion step. The full burnup time of the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ $36$ $pcm$. The online extraction of \gls{FPs} and noble gases  provides many benefits for MSRs. For example, it would reduce the fissile inventory required to achieve criticality and improve the breeding ratio.
Figure~\ref{fig:flow} shows a flow chart of the calculation steps.

@@

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time. This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the \texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}. Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the isotopes during reactor operation \cite{aufiero2013extended}. The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle. Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.

\section{Feed and extraction rates}
In the present work, two different feed mechanisms are used. The first mechanism allows continuous feed flow of thorium and $^{233}$U from \texttt{pa-decay tank}. In contrast, the second mechanism adopts continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.\\
The fission products act as poisons in the MSRs; they negatively impacting the reactivity. Therefore, \gls{FPs} must be extracted during reactor operation. Consider $T_{r}$ as the time during which the total fuel salt is reprocessed and $dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}

@@

\begin{table}[ht!]
	\centering
	\caption{The reprocessing table.} 
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|s|p{2cm}|}
			\hline
			\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reproc- essing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
			\hline
			Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au and Rn.		&	30s	&  -3.333E-02 \\
			\hline
			Lanthanides and other soluble \gls{FPs}     & 
			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm and Yb. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
			\hline
			Protactinium   & Pa  &  10.599 d (5 m$^3$/d)  &  -1.092E-06 \\
			\hline
	\end{tabularx}
	\label{tab:table6}
\end{table}
